---
title: "Introduction to StatComp20083"
author: "Pengyi Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20083}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Overview

__StatComp__ is my homework and some function that I wrote it myself. The purpose of my function is to select an optimal bandwidth in a set of response variables with a double-truncated function variable data.


## Benchmarking

These are my function:

Kernel() is a kernel.
```{r,eval=FALSE}
Kernel=function(x)
{
  h=1/sqrt(2*3.14159)*exp(-x^2/2)
  return(h)
}
```
d() is a measure function.
```{r,eval=FALSE}
d=function(x1,x2)
{
  x3=x1-x2
  fff=function(x){(x3[1]+x3[2]*x+x3[3]*x^2+x3[4]*x^3+x3[5]*x^4)^2}    
  return(sqrt(as.numeric(integrate(fff,0,1)[1])))
}
```
GnS() is a function that handles the effects of truncation data.
```{r,eval=FALSE}
GnS=function(x)    # x=(Y,U,V)
{
  n=nrow(x)
  H=1:n
  h1=1:n
  h2=1:n
  F=1:n
  f=1:n
  I=function(t)
  {
    if(t[2]<=t[1]&t[1]<=t[3]){return(1)}
    else {return(0)}
  }
  for(i in 1:n){h1[i]=1/n}
  for(i in 1:n)
  {
    H[i]=0
    for(j in 1:n){H[i]=H[i]+h1[j]*I(c(x[j,1],x[i,2],x[i,3]))}
  }
  while(abs(max(h1-h2))>=10^(-6))
  {
    h2=h1
    for(j in 1:n)
    {
      f[j]=0
      for(i in 1:n){f[j]=f[j]+1/H[i]}
      f[j]=(1/f[j])*(1/H[j])
    }
    for(i in 1:n)
    {
      F[i]=0
      for(j in 1:n){F[i]=F[i]+f[j]*I(c(x[i,1],x[j,2],x[j,3]))}
    }
    for(j in 1:n)
    {
      h1[j]=0
      for(i in 1:n){h1[j]=h1[j]+1/F[i]}
      h1[j]=(1/h1[j])*(1/F[j])
    }
    for(i in 1:n)
    {
      H[i]=0
      for(j in 1:n){H[i]=H[i]+h1[j]*I(c(x[j,1],x[i,2],x[i,3]))}
    }
  }
  return(f)
}
```
creat() is a function that makes GnS() easy to use.
```{r,eval=FALSE}
creat=function(Y,U,V){
  n=length(Y)
  US=matrix(1,nrow=n,ncol=3)
  US[,1]=Y;US[,2]=U;US[,3]=V
  TS=GnS(US)
  Gn=function(y)
  {
    h=0
    for(j in 1:n){if(U[j]<=y&&y<=V[j]){h=h+TS[j]}}
    return(h)
  }
  return(Gn)
}
```
It is the final cross validation function
```{r,eval=FALSE}
CV=function(X,Y,U,V,h1)
{
  Gn=creat(Y,U,V)
  n=nrow(X)
  mNW=function(x,h,y,x1)
  {
    n1=nrow(x)
    f1=0
    f2=0
    for(i in 1:n1){f1=f1+Kernel(d(x1,x[i,])/h)*y[i]/Gn(y[i])}
    for(i in 1:n1){f2=f2+Kernel(d(x1,x[i,])/h)/Gn(y[i])}
    return(f1/f2)
  }
  CVH=function(x,h,y)
  {
    f3=0
    n2=nrow(x)
    for(i in 1:n2){f3=f3+(y[i]-mNW(x[-i,],h,y[-i],x[i,]))^2}
    return(f3)
  }
  y=rep(1,length(h1))
  for(j in 1:length(h1)){y[j]=CVH(X,h1[j],Y)}	
  place=which(y==min(y))
  h=h1[place]
  return(h)
}

```

now let's see what it does

```{r}
library(StatComp20083)
n=100 
m=5    
max=1
min=0
i=1   
fangcha=0.01 
X=matrix(-1,nrow=n,ncol=m)
Y=rep(-1,n);U=Y;V=Y
while(Y[n]==-1)
{
  X[i,]=runif(m,min=min,max=max)
  gt=function(x){X[i,1]+X[i,2]*x+X[i,3]*x^2+X[i,4]*x^3+X[i,5]*x^4}
  y=as.numeric(integrate(gt,0,1)[1])+rnorm(1,mean=0,sd=fangcha)
  u=runif(1,min=-0.5,max=1.15);v=runif(1,min=1.15,max=2.8)
  if(u<=y&&y<=v){Y[i]=y;U[i]=u;V[i]=v;i=i+1}
}
rm(y)
Gn=creat(Y,U,V)
h1=seq(0.1,2,0.1)
h=CV(X,Y,U,V,h1)
print(h)
h1=seq(max(0.01,h-0.1),h+0.1,0.01)
h=CV(X,Y,U,V,h1)
print(h)
h1=seq(max(0.001,h-0.01),h+0.01,0.001)
h=CV(X,Y,U,V,h1)
print(h)
h1=seq(max(0.0001,h-0.001),h+0.001,0.0001)
h=CV(X,Y,U,V,h1)
print(h)
```